Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Added paragraphs to medels section

Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach. Statistical methods assume that the importance of a word/sentence in a text depends on the number of times the word/sentence appears in the document. This means that this classical approach ignores context and lexical features of the text. Furthermore, they are able to perform only extractive summarization. Graph models find similarity between words/sentences in the whole text, which is used as weight of the graph edge. While proving to have better results than simple frequency-based methods, they are still bounded by the absence of lexic understanding and ability to  perform extractive summary only. 
In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization. Using encoder-decoder models it is now possible to produce abstract summaries. In [https://arxiv.org/pdf/1602.06023.pdf] the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state of-the-art systems on two different English corpora. However, there is not much of information about neural networks usage in scientific text summarization.

>>>>

Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.

\paragraph{Statistical methods} assume that the importance of a word or sentence in a text depends on the number of times the word/sentence appears in the document. This means that this classical approach ignores context and lexical features of the text. Furthermore, they are able to perform only extractive summarization.

\paragraph{Graph models} find similarity between words/sentences in the whole text, which is used as weight of the graph edge. While proving to have better results than simple frequency-based methods, they are still bounded by the absence of lexic understanding and ability to  perform extractive summary only.

\paragraph{Machine learning approach} In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization. Using encoder-decoder models it is now possible to produce abstract summaries. In [https://arxiv.org/pdf/1602.06023.pdf] the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state of-the-art systems on two different English corpora. However, there is not much of information about neural networks usage in scientific text summarization.
